Filter check

### 2019-01-04 R/filter-check.Rmd
Demultiplex and quality filter.  Uses parallel processing in demultiplex_all.R, but the parallel BLAST doesn't seem to work.

if (interactive()) {
  base.dir <- getwd() %>%
    str_extract(".*oueme-fungi-transect")
  data.dir <- file.path(base.dir, "data")
  lab.dir <- file.path(data.dir, "lab_setup")
  gits7.file <- file.path(lab.dir, "Hectors tag primer plates.xlsx")
  its1.lr5.file <- file.path(lab.dir, "Brendan soil2.xlsx")
  tag.files <- list.files(file.path(lab.dir, "tags"), ".+\\.fasta", full.names = TRUE)
  pacbio.dir <- file.path(data.dir, "PacBio")
  pacbio.fastq.files <- list.files(pacbio.dir, "\\.fastq\\.gz", full.names = TRUE)
  in.name <- "pb_500_001"
  in.fastq <- file.path(pacbio.dir, "pb_500_001.reads_of_insert.fastq.gz")
  in.fwd <- str_replace(in.fastq, fixed(".fastq.gz"), ".gits7.blast")
  in.rev <- str_replace(in.fastq, fixed(".fastq.gz"), ".primer.blast")
  out.fastq <- str_replace(in.fastq, fixed(".fastq.gz"), ".demux.fastq.gz")
  out.groups <- str_replace(in.fastq, fixed(".fastq.gz"), ".groups")
  platekey <- file.path(lab.dir, "gITS7_platekey.csv")
  plate <- "short_002"
}
```

```{r}
fastq <- readFastq(out.fastq)
qual <- tibble(
  eexp = 10^(-1 * as(fastq@quality, "matrix")/10) %>%
  rowSums(na.rm = TRUE),
  length = width(fastq),
  erate = eexp/length)

ggplot(qual, aes(x = erate)) +
  stat_ecdf(geom = "step") +
  scale_x_log10(name = "Expected number of errors per base") +
  scale_y_continuous(name = "Fraction passing")

ggplot(qual, aes(x = eexp)) +
  stat_ecdf(geom = "step") +
  scale_x_log10(name = "Expected number of errors") +
  scale_y_continuous(name = "Fraction passing")

ggplot(qual, aes(x = length)) +
  stat_ecdf(geom = "step") +
  scale_x_log10(name = "Length (bp)") +
  scale_y_continuous(name = "Fraction Greater than length")

>>>>

if (interactive()) {
  base.dir <- getwd() %>%
    str_extract(".*oueme-fungi-transect")
  data.dir <- file.path(base.dir, "data")
  lab.dir <- file.path(data.dir, "lab_setup")
  seq.dir <- file.path(base.dir, "raw_data")
  dataset.file <- file.path(lab.dir, "datasets.csv")
  datasets <- read_csv(dataset.file) %>%
    mutate(demux.dir = file.path(seq.dir, Dataset, Seq.Run, "demultiplex"),
           files = map(demux.dir, list.files, pattern = "*.fastq.gz",
                       full.names = TRUE)) %>%
    unnest() %>%
    mutate(filesize = file.size(files)) %>%
    filter(filesize > 0) %>%
    mutate(fastq = map(files, readFastq),
           eexp = map(fastq, ~ 10^(-1 * as(.@quality, "matrix")/10) %>%
                        rowSums(na.rm = TRUE)),
           length = map(fastq, width)) %>%
    select(-fastq) %>%
    unnest %>%
    mutate(erate = eexp/length)
}
```

```{r}
ggplot(datasets, aes(x = erate, group = Dataset, color = Dataset)) +
  stat_ecdf(geom = "step") +
  scale_x_log10(name = "Expected number of errors per base") +
  scale_y_continuous(name = "Fraction passing")

ggplot(datasets, aes(x = eexp, group = Dataset, color = Dataset)) +
  stat_ecdf(geom = "step") +
  scale_x_log10(name = "Expected number of errors") +
  scale_y_continuous(name = "Fraction passing")

ggplot(datasets, aes(x = length, group = Dataset, color = Dataset)) +
  stat_ecdf(geom = "step") +
  scale_x_log10(name = "Length (bp)") +
  scale_y_continuous(name = "Fraction Greater than length")
